Multi-Core Model Checking and Maximum Satisfiability Applied to Hardware-Software Partitioning

### 2016-08-20 Docs/IJES/journal.tex
replying some comments

Consequently, the second approach aims to remove the idle time from the parallel loops, by creating workers inside threads so that the next step is immediately executed if there is a processing core available, as shown in Fig.~\ref{ESBMC-Multi-core-Optimized-Sequential-Approach}. This approach could potentially lead to great performance improvements, but as ESBMC checks for each step almost at the same rate, the processor does not remain idle for a longer period and thus there is almost no optimization.

@@

The arithmetic expressions from lines $10$ to $12$ represent the constraints described in Eq.~\eqref{hw-sw-partitioning}. Here, variable \textit{SC} refers to the software cost, while \textit{CC} denotes the communication cost. In line $12$, the \textit{Fobj} (objective function) is declared, which denotes the product between the hardware cost and the decision variables vector, which contains only Boolean values. \textit{Fobj} should be minimized to obtain the optimal hardware solution. To achieve this, two constraints are imposed to ESBMC-$\nu$Z: the first one refers to the sum of the software and communication costs, where the result should be less than $S_0$; and the second one instructs to ESBMC-$\nu$Z that \textit{Fobj} should be minimized. Finally, the model is checked by ESBMC-$\nu$Z and if there is a solution that 
meets the constraints, then the \textit{Fobj} value is provided.

>>>>

\textcolor{blue}{In contrast to ESBMC-SS, the second approach aims to remove the idle time from the parallel loops, by creating workers inside threads so that the next step is immediately executed if there is a processing core available, as shown in Fig.~\ref{ESBMC-Multi-core-Optimized-Sequential-Approach}. In addition, there is no communication among the workers, but each worker notifies the controller if a violation is found for its TipH value}.

%This approach could potentially lead to great performance improvements, %but as ESBMC checks for each step almost at the same rate, the processor does not remain idle for a longer period and thus there is almost no optimization.

@@

The arithmetic expressions from lines $10$ to $12$ represent the constraints described in Eq.~\eqref{hw-sw-partitioning}. Here, variable \textit{SC} refers to the software cost, while \textcolor{blue}{\textit{CMC}} denotes the communication cost. In line $12$, the \textit{Fobj} (objective function) is declared, which denotes the product between the hardware cost and the decision variables vector, which contains only Boolean values. \textit{Fobj} should be minimized to obtain the optimal hardware solution. To achieve this, two constraints are imposed to ESBMC-$\nu$Z: the first one refers to the sum of the software and communication costs, where the result should be less than $S_0$; and the second one instructs to ESBMC-$\nu$Z that \textit{Fobj} should be minimized. Finally, the model is checked by ESBMC-$\nu$Z and if there is a solution that 
meets the constraints, then the \textit{Fobj} value is provided.
